On the performance of the MAC model

### 2018-10-29 2018_nips_vigil/introduction.tex
correct typo

The Visual Question Answering (VQA) task has been tailored to benchmark those reasoning performances. It is a complex semantic task requiring both natural language processing and visual recognition. It also put to the test the effective use of the short term memory.

@@

In this work, we first question the complexity of the MAC model and explore simplification possibilities. We propose a new set of equations that aims to simplify the model and improve training performance. 
We also put to proof the MAC model on the CLEVR CoGenT dataset. The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability. By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned. We show how MAC performs on CLEVR CoGenT and compare it to state-of-the-art models.
and propose a study about the model failures. This work points out some of the MAC model weaknesses, in particular its failure to differentiate concepts of colors and shape. We finally discuss some improvement possibilities.

>>>>

The Visual Question Answering (VQA) task has been tailored to benchmark those reasoning performances. It is a complex semantic task requiring both natural language processing and visual recognition. It also puts to the test the effective use of the short term memory.

@@

In this work, we first question the complexity of the MAC model and explore simplification possibilities. We propose a new set of equations that aims to simplify the model and improve training performance. 
We also put to proof the MAC model on the CLEVR CoGenT dataset. The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability. By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned. We show how MAC performs on CLEVR CoGenT and compare it to state-of-the-art models and propose a study about the model failures. This work points out some of the MAC model weaknesses, in particular its failure to differentiate concepts of colors and shape. We finally discuss some improvement possibilities.
